Discordance LV - TF

### 2024-08-07 reporting/discordance_previous_results/discordance LV TF.Rmd
reorganise folders

```{r eval=TRUE, fig.cap="Original plot", fig.height=6, echo=FALSE}
knitr::include_graphics("images/comparison_methods6-1.png")
```

@@

```{r eval=TRUE, fig.cap="New plot (fails to replicate)", fig.height=6, echo=FALSE}
knitr::include_graphics("images/plot_original.png")
```

>>>>

```{r eval=TRUE, fig.cap="Original plot", fig.height=6, echo=FALSE}
knitr::include_graphics(here::here("images/comparison_methods6-1.png"))
```

@@

```{r eval=TRUE, fig.cap="New plot (fails to replicate)", fig.height=6, echo=FALSE}
knitr::include_graphics(here::here("images/plot_original.png"))
```
